\sys: Light-touch Data-Parallel Shell Processing

### 2020-05-16 evaluation/plots/microbenchmarks-table.tex
New plots and table based on new results

\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} lllllll}
\toprule
Script ~&~ Structure & Input &Seq Time & Script Size(16, 64) &Compile Time (16, 64) & Highlights \\
\midrule
\tti{grep} ~&~ $3\times$\tsta & 1~GB & 79m41.137s & \todo{\#Commands} & 0.050s\qquad 0.417s & complex NFA regex \\
\tti{sort} ~&~ $\tsta, \tpur$ & 10~GB & 21m27.510s & \todo{\#Commands} & 0.076s\qquad 0.839s & \tti{sort}ing \\
\tti{top-n} ~&~ $2\times\tsta, 4\times\tpur$ & 10~MB & 73m28.098s & \todo{\#Commands} & 0.119s\qquad 1.407s & double \tti{sort}, \tti{uniq} reduction \\
\tti{wf} ~&~ $3\times\tsta, 3\times\tpur$ & 10~GB & 22m26.670s & \todo{\#Commands} & 0.121s\qquad 1.388s & double \tti{sort}, \tti{uniq} reduction \\
\tti{grep-light} ~&~ $3\times$\tsta & 100~GB & 1m38.212s & \todo{\#Commands} & 0.031s\qquad 0.163s & 	odo{light computation} \\
\tti{spell} ~&~ $4\times\tsta, 3\times\tpur$ & 1~GB & 8m9.370s & \todo{\#Commands} & 0.214s\qquad 2.800s & comparisons (\tti{comm}) \\
\tti{shortest-scripts} ~&~ $5\times\tsta, 2\times\tpur$ & 85~MB & 28m25.818s & \todo{\#Commands} & 0.210s\qquad 2.762s & \todo{extensive file-system operation} \\
\tti{diff} ~&~ $2\times\tsta, 3\times\tpur$ & 10~GB & 25m10.092s & \todo{\#Commands} & 0.254s\qquad 1.958s & non-parallelizable \tti{diff}ing \\
\tti{optimized bi-grams} ~&~ $3\times$\tsta, \tpur & 10~MB & 125m10.224s & \todo{\#Commands} & 0.098s\qquad 1.171s & optimized version of bigrams \\
\tti{set-diff} ~&~ $5\times\tsta, 2\times\tpur$ & 10~GB & 51m22.068s & \todo{\#Commands} & 0.250s\qquad 3.316s & two pipelines merging to a \tti{comm} \\
\bottomrule
\end{tabular*}

>>>>

\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} lllllll}
\toprule
Script ~&~ Structure & Input &Seq Time & \#Nodes(16, 64) &Compile Time (16, 64) & Highlights \\
\midrule
\tti{grep} ~&~ $3\times\tsta$ & 1~GB & 79m35.197s & 49\qquad 193 & 0.056s\qquad 0.523s & complex NFA regex \\
\tti{sort} ~&~ $\tsta, \tpur$ & 10~GB & 21m46.807s & 77\qquad 317 & 0.090s\qquad 1.083s & \tti{sort}ing \\
\tti{top-n} ~&~ $2\times\tsta, 4\times\tpur$ & 10~GB & 78m45.872s & 96\qquad 384 & 0.145s\qquad 1.790s & double \tti{sort}, \tti{uniq} reduction \\
\tti{wf} ~&~ $3\times\tsta, 3\times\tpur$ & 10~GB & 22m30.048s & 96\qquad 384 & 0.147s\qquad 1.809s & double \tti{sort}, \tti{uniq} reduction \\
\tti{grep-light} ~&~ $3\times\tsta$ & 100~GB & 1m38.212s & \todo{X}\qquad \todo{X} & 0.031s\qquad 0.163s & \todo{light computation} \\
\tti{spell} ~&~ $4\times\tsta, 3\times\tpur$ & 1~GB & 8m1.428s & 69\qquad 261 & 0.104s\qquad 1.060s & comparisons (\tti{comm}) \\
\tti{shortest-scripts} ~&~ $5\times\tsta, 2\times\tpur$ & 85~MB & 28m45.900s & 142\qquad 574 & 0.328s\qquad 4.657s & \todo{extensive file-system operation} \\
\tti{diff} ~&~ $2\times\tsta, 3\times\tpur$ & 10~GB & 25m49.097s & 125\qquad 509 & 0.186s\qquad 2.341s & non-parallelizable \tti{diff}ing \\
\tti{optimized bi-grams} ~&~ $3\times\tsta, \tpur$ & 3~GB & 38m21.501s & 63\qquad 255 & 0.117s\qquad 1.482s & optimized version of bigrams \\
\tti{set-diff} ~&~ $5\times\tsta, 2\times\tpur$ & 10~GB & 51m32.313s & 155\qquad 635 & 0.321s\qquad 4.358s & two pipelines merging to a \tti{comm} \\
\tti{sort-sort} ~&~ $\tsta, 2\times\tpur$ & 10~GB & 31m26.147s & 78\qquad 318 & 0.092s\qquad 1.077s & parallelizable \tpur after \tpur \\
\bottomrule
\end{tabular*}

### 2020-05-16 pldi/draft.tex
Comment about PAL grammar
Minor note
New plots and table based on new results

@@

    \begin{subfigure}[b]{0.24\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/topn_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:topn}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.24\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/wf_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:wf}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.24\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/shortest_scripts_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:spell}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.24\textwidth}
      \centering
      \includegraphics[width=\textwidth]{\detokenize{./figs/alt_bigrams_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:minimal_sort}
    \end{subfigure}%
    \caption{
      \textbf{Speedup achieved by \sys as a function of the level of parallelism (1--100).} 
      Four different configurations per benchmark:
      (i) \todo{Parallel}, showing the performance of \sys with both eager and split optimizations enabled,
      (ii) \todo{No Split}, showing the performance of \sys with split disabled,
      (iii) \todo{No Eager}, showing the performance of \sys with split and eager disabled,
      (iv) \todo{Blocking Eager}, showing the performance of \sys with split disabled and the naive blocking eager enabled,
      \nv{Maybe it makes sense to show log x-axis?}
    }
    \vspace{-15pt}
    \label{fig:microbenchmarks}
\end{figure*}

\heading{Programs}
Tab.~\ref{tab:eval} summarizes the collection of micro-benchmarks used to evaluate \sys.
Benchmark names (col. 1) correspond to the names on the plots (Fig.~\ref{fig:microbenchmarks}), and structure (col. 2) summarizes the different classes of commands used in the script.
% The centralized pipelines read files of various sizes from disk and write to disk.
Input sizes and times (col. 3, 4) summarize the characteristics of the largest sequential executions. % (200 files in Fig.~\ref{fig:microbenchmarks}).
Script sizes (col. 5) report on \sys's rewritten output for three different distribution sizes---$1\times$, 10$\times$, and $100\times$.
Size grows due to the resulting complexity of coordinating among parallel executions---multiple FIFOs per pipeline stage, merging and splitting, encoding of divide-and-conquer synchronization \etc
The first number alone is interesting, as it captures \sys's output for the sequential script.
As there is no parallelism involved, it highlights the initial (bare minimum) cost corresponding to using \sys.
% this is the size of 
This change in size does not necessarily translate to observed runtime, as most of the size increase comes from the setup and teardown of FIFOs responsible for interprocess (IPC) communication.
FIFOs are simply pipes made explicit;
  the performance characteristics, including in-kernel buffering and synchronization mechanisms, are identical between the two.

>>>>

\kk{We could add the grammar of PAL in an appendix if we want}

@@

    \begin{subfigure}[b]{0.24\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/topn_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:topn}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.24\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/wf_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:wf}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.24\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/shortest_scripts_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:spell}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.24\textwidth}
      \centering
      \includegraphics[width=\textwidth]{\detokenize{./figs/alt_bigrams_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:minimal_sort}
    \end{subfigure}%
    \caption{
      \textbf{Speedup achieved by \sys as a function of the level of parallelism (1--100).} 
      Four different configurations per benchmark:
      (i) \todo{Parallel + Split}, showing the performance of \sys with both eager and split optimizations enabled,
      (ii) \todo{Parallel}, showing the performance of \sys with eager enabled and split disabled,
      (iii) \todo{No Eager}, showing the performance of \sys with split and eager disabled,
      (iv) \todo{Blocking Eager}, showing the performance of \sys with split disabled and the naive blocking eager enabled,
      \nv{Maybe it makes sense to show log x-axis?}
      \kk{How can we also fit two more plots (sort-sort and diff) here? Maybe we can fit one by getting rid of sort (since it also shown in the sort--parallel one). Otherwise we could separate the ``split'' plots from the ones that don't have split.}
    }
    \vspace{-15pt}
    \label{fig:microbenchmarks}
\end{figure*}

\heading{Programs}

\kk{How can we include a result for grep-light?  This is the IO
  intensive CPU-light grep. \sys has no speedup but also no slowdown
  (even if it IO heavy). Should we just mention that in text in
  passing?}

Tab.~\ref{tab:eval} summarizes the collection of micro-benchmarks used to evaluate \sys.
Benchmark names (col. 1) correspond to the names on the plots (Fig.~\ref{fig:microbenchmarks}), and structure (col. 2) summarizes the different classes of commands used in the script.
% The centralized pipelines read files of various sizes from disk and write to disk.
Input sizes and times (col. 3, 4) summarize the characteristics of the largest sequential executions. % (200 files in Fig.~\ref{fig:microbenchmarks}).
Script sizes (col. 5) report on \sys's rewritten output for three different distribution sizes---$1\times$, 10$\times$, and $100\times$.
Size grows due to the resulting complexity of coordinating among parallel executions---multiple FIFOs per pipeline stage, merging and splitting, encoding of divide-and-conquer synchronization \etc
The first number alone is interesting, as it captures \sys's output for the sequential script.
As there is no parallelism involved, it highlights the initial (bare minimum) cost corresponding to using \sys.
% this is the size of 
This change in size does not necessarily translate to observed runtime, as most of the size increase comes from the setup and teardown of FIFOs responsible for interprocess (IPC) communication.
FIFOs are simply pipes made explicit;
  the performance characteristics, including in-kernel buffering and synchronization mechanisms, are identical between the two.
